\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
updated eye-tracking literature for HRI

Several scholars related gaze patterns with level of expertise.
\cite{hasse2012measure} in an air traffic-monitoring task found out that the
experts looked less at the scenario-specific information than novices.
\cite{eivazi2012gaze, law2004eye, tien2010measuring} studied the effect of
expertise on the gaze patterns in different surgical tasks and concluded that
experts look less at the instruments than the novices, instead they focus more
on the task specific areas. \cite{reingold2001visual} showed that expert chess
players pay more attention to the relative positions of the pieces, rather than
the individual pieces, than novice chess players. \cite{blignaut2008visual} also
studied the difference between experts and novice chess players in a checkmate
avoidance task and concluded that the experts have more gaze falling on the
important squares than the novices. In a program-debugging task,
\cite{sharif2012eye} showed that the expert programmers scan through all the
lines in the program faster than the novices. In a collaborative Tetris game,
\cite{jermann2010using} showed that experts pay more attention to the stack of
Tetronimoes while novices allocate more attention to the new pieces falling from
the top.

\subsection{Gaze patterns and Collaborative work}

Our previous work also show a clear relation between gaze patterns and
task-based performance. In a pair-programming task, \cite{jermann2012effects}
showed that the good performing pairs have more synchronised gaze on different
parts of a program than the bad performing pairs. In a similar task,
\cite{sharma2012gaze} showed that the good performing pairs pay more attention
to the data-flow of the program than the poor performing pairs. Moreover,
\cite{sharma2013understanding} showed that while describing the functionality of
a program the well performing teams had more gaze on the variable modification
parts in the program while poor performing teams have equal distribution of gaze
on different parts of the program during similar phase of the task.  Thus we see
that previous research provides insights about the relationship between the gaze
patterns and the behavioural and task-based performance indicators in diverse
scenarios.

@@

@@

\subsection{Eye Tracking as a tool to Measure Joint Attention}

It must be noted that to our best knowledge only very few studies have
investigated how eye-tracking could be used to assess HRI. In an eye-tracking
study, in the context of human robot interaction, \cite{staudte2009visual} found
that when the robot provides a matching visual and verbal reference to an object
the participants were more likely to look at the correct objects. This result
was consistent irrespectively of the ambiguity of the situation. 
SAY ABOUT THE VIDEO BASED INTERACTION

>>>>

Several scholars related gaze patterns with level of expertise.
\cite{hasse2012measure} in an air traffic-monitoring task found out that the
experts looked less at the scenario-specific information than novices.
\cite{eivazi2012gaze, law2004eye, tien2010measuring} studied the effect of
expertise on the gaze patterns in different surgical tasks and concluded that
experts look less at the instruments than the novices, instead they focus more
on the task specific areas. \cite{reingold2001visual} showed that expert chess
players pay more attention to the relative positions of the pieces, rather than
the individual pieces, than novice chess players. \cite{blignaut2008visual} also
studied the difference between experts and novice chess players in a checkmate
avoidance task and concluded that the experts have more gaze falling on the
important squares than the novices. In a program-debugging task,
\cite{sharif2012eye} showed that the expert programmers scan through all the
lines in the program faster than the novices. In a Tetris game,
\cite{jermann2010using} showed that experts pay more attention to the stack of
Tetronimoes while novices allocate more attention to the new pieces falling from
the top.

\subsection{Gaze patterns and Collaborative performance}

Previous work also show a clear relation between gaze patterns and
task-based performance in collaborative settings. 
CITE RICK DALE

In a pair-programming task, \cite{jermann2012effects}
showed that the good performing pairs have more synchronised gaze on different
parts of a program than the bad performing pairs. In a similar task,
\cite{sharma2012gaze} showed that the good performing pairs pay more attention
to the data-flow of the program than the poor performing pairs. Moreover,
\cite{sharma2013understanding} showed that while describing the functionality of
a program the well performing teams had more gaze on the variable modification
parts in the program while poor performing teams have equal distribution of gaze
on different parts of the program during similar phase of the task.  Thus we see
that previous research provides insights about the relationship between the gaze
patterns and the behavioural and task-based performance indicators in diverse
scenarios.

@@

The literature on the

@@

\subsection{Eye Tracking as a tool to Assess Interaction Algorithms}

Physiological and subjective evaluation of a human?robot object hand-over task

\subsection{Eye Tracking as a tool to Assess Joint Attention}

It must be noted that to our best knowledge only very few studies have
investigated how eye-tracking could be used to assess HRI. In an eye-tracking
study, in the context of human robot interaction, \cite{staudte2009visual} found
that when the robot provides a matching visual and verbal reference to an object
the participants were more likely to look at the correct objects. This result
was consistent irrespectively of the ambiguity of the situation.
